#1. Load the data (i.e. ğš›ğšğšŠğš.ğšŒğšœ
```{r}
cpw1 <- read.csv("activity.csv")
#explore dataset
names(cpw1)
head(cpw1)
dim(cpw1)
summary(cpw1)
```
#2. Calculate the total number of steps taken per day
```{r}
cpds <- tapply(cpw1$steps, cpw1$date, sum, na.rm=TRUE)
```
#3. Histogram of steps taken by day
```{r}
hist(cpds, col="blue", main="Steps Taken Each Day", xlab="steps", ylab="day")
#plot.png in the home page of this repo. Its not printing in the markdown here, but it works in R.
```
#4. Calculate and report the mean and median of the total number of steps taken per day
```{r}
mean(cpds)
#9354.23
median(cpds)
#10395
```
#5. Make a time series plot (i.e. ğšğš¢ğš™ğš = "ğš•") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
df2 <- tapply(cpw1$steps, cpw1$interval, mean, na.rm=TRUE)
plot(df2, col="blue", type="l", xlab="interval", ylab="steps", main="Steps done by interval")
#plot1.png in the home page of this repo. Its not printing in the markdown here, but it works in R.
```
#6. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
which.max(df2)
#835
#206.1698
```
#7. Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with ğ™½ğ™°s)
```{r}
sum(is.na(cpw1))
```
#8. Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc. Create a new dataset that is equal to the original dataset but with the missing data filled in.
```{r}
cpw1_new <- cpw1  # creation of the dataset that will have no more NAs
for (i in 1:nrow(cpw1)){
  if(is.na(cpw1$steps[i])){
    cpw1_new$steps[i]<- df2[[as.character(cpw1[i, "interval"])]]
  }
}
```
#9. Make a histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day. 
```{r}
cpds_new <- tapply(cpw1_new$steps, cpw1_new$date, sum, na.rm=TRUE)
head(cpds_new)
head(cpds)
dim(cpds_new)
dim(cpds)
```
#10. What is the impact of imputing missing data on the estimates of the total daily number of steps? Do these values differ from the estimates from the first part of the assignment?
```{r}
equality <- (cpds == cpds_new)
equality_new <- replace(equality, isTRUE(equality), 1)
mean(equality_new)
#0.8688
1 - 0.8688
#0.1312; the missing values affect in 13.12% the previous dataset
```
#11. Histogram of steps taken by day
```{r}
hist(cpds_new, col="red", main="Steps Taken Each Day with NAs replaced", xlab="steps", ylab="day")
#plot2.png in the home page of this repo. Its not printing in the markdown here, but it works in R.
```
```{r}
```
#12. Calculate mean and median
```{r}
mean(cpds_new)
#10766.19
median(cpds_new)
#10766.19
```
#12. Are there differences in activity patterns between weekdays and weekends?
```{r}
library(ggplot2)
library(plyr)
paindays= c("Monday","Tuesday","Wednesday","Thursday","Friday")

cpds$weekday<-as.factor(ifelse(weekdays(cpds$date)%in%paindays,"weekday","weekend"))

stepsperinterval.weekdaysplit<-ddply(cpds_new, c("interval","weekday"),summarise,
                    meansteps = mean(steps,na.rm=TRUE)
)

weekday_plot<-ggplot(stepsperinterval.weekdaysplit,aes(x=interval,y=meansteps))+
  facet_wrap(~weekday,nrow=2,ncol=1)+
  geom_line()+
  theme_bw()+
  ggtitle("Mean steps over each 5min interval split by weekday/weekend")+
  ylab("Mean steps")+
  xlab("Interval number")
print(weekday_plot)
```
